### 2004-11-16 doc/Simulation_and_Control_using_Supremica/automationobjects.tex
*** empty log message ***

Configuration registry is a function block implementing the
configuration database and interface to it. This
function block holds all relevant attributes for the
automation object and provides an interface for accessing
and changing them. Configuration registry is used by models,
controllers and the views for storing and retrieving the
configuration data.

@@

\section{Implementation and Support in Supremica}
% Support in Supremica
First implementation of the automation object concepts will
be done in the Supremica. The architecture for the
automation objects will be concurrently implemented with the
development tools and functions. In this section
implementation considerations are discussed and the
development work flow is presented using some mockup
screenshots.

%% implementation of automation objects
%%   archive of XML files
%%   models, views, controllers and registry are declared in
%%   some kind of MetaInformation.xml 
An automation object is distributed as compressed archive of
XML-files. The archive contains XML definitions of models,
views, controllers, registry and a file containing the meta
information for the automation object. In the meta
information file all information about the automation object
(ie name, creator, version), all of the possible
configuration attributes, service definitions and interface
explanations are stored.

%% libraries 
%%   non-hierarchical pool of automation objects
%%   libraries  may be Internet repositories
%%   searching and sorting by multiple attributes/keys
%%   searching and sorting by services

%% development tool is the control system
%% how will it work (mockups)

>>>>

Configuration registry is a function block implementing the
configuration database and interface to it. This function
block holds all relevant attributes and configuration
variables for the automation object and provides an
interface for accessing and changing them. Configuration
registry is used by models, controllers and the views for
storing and retrieving the configuration data. For example,
controllers will use this function block to access their
regulator parameters and other configurable parameters.

@@

\section{Implementation and Support in Supremica}
% Support in Supremica
First implementation of the automation object concepts will
be done in the Supremica. The architecture for the
automation objects will be concurrently implemented with the
development tools and functions. In this section
implementation considerations are discussed and the
development work flow is presented.

%% format of automation objects
%%   archive of XML files
%%   models, views, controllers and registry are declared in
%%   some kind of MetaInformation.xml 
An automation object is distributed as compressed archive of
XML-files. The archive contains XML definitions of models,
views, controllers, registry and a file containing the meta
information for the automation object. In the meta
information file all the automation object attributes
(ie name, creator, version), all of the possible
configuration variables, service definitions and interface
explanations are stored. In other words everything needed
for successful reusage in the development, configuration and
execution of the automation object.

%% repositories
%%   non-hierarchical pool of automation objects
%%   may be share using the internet
%%   searching and sorting by multiple attributes/keys
%%   searching and sorting by services
It is envisioned that after the initial acceptance period
significant amount of automation objects are developed.
These are stored in the repositories for easy acess. The
repositories are non-hierarchical pools of automation
objects, probably implemented using database technology.
These repositories are prefferably shared over the internet.
The most important feature of the repositories is the
ability for extensinve search and sorting by multiple
attributes defined in the registry as well as the defined
services.

%% development tool is the control system
%% how will it work?
The Supremica tool provides the user interface for the
development and the deployment of the automation object
applications. The implementation that supports the user
interface consists of two cooperating parts. The development
environment for the automation objects and the run-time
environment for the function blocks.

The DE provides the tools and functions for the repository
handlig and automation object development. The user is able
to choose among the available automation objects from the
repository and include them in the application. While
working with the objects the user can activate different
services or bring up specific views and exchange the models
and controllers. User can also connect the views of the
different objects in the application. Working in this way
the user can build and tune the application to it's liking.

All the time during the development process the run-time
environment is active and taking commands from the
development environment to add function block types, add
instances and connections to composite function block types,
to add instances and connections to the application, to
configure the resources, to start and stop the execution of
the application and so, thus creating the application in the
run-time environment as it is developed. These commands are
all at the function block level. It is the development
environment that transforms the automation object operations
into the function blocks running in the run-time environment
and thus making all of the automation objects alive
throughout the development.

While the user have one of the simulation models activated
the run-time is executing the code that simulates the
behaviour of the hardware that the object is supposed to
control. Switching to the model that talks to the process
interface issues a command to exchange the function blocks
in the run-time and results in the control of hardware
instead of the simulation of the control. This gives user
the freedom to incrementally develop large systems.

For example, consider a production plant that is connected
to the network of control computers. Engineers responsible
for each part can develop, tune and test their part on any
computer on the network. As each one switches to the model
that communcates with the hardware the plant becomes more
and more functional until it is fully operational.

To accomplish this the development environment uses the
database technology to hold the application data that is
shared. While working on the application the engineers can
acess this data from any computer on the network. The
application data includes the distribution configuration
governing which automation objects are run by which
computers on the network. By issuing the commands to the
run-time environment of the computer running the automation
object that is currently worked on, the development
environment allows the user to work on the whole application
from any computer on the network. This means that if
something goes wrong or software/equipment needs upgrading
anyone that can acess the application data can, from any
computer on the network, switch the model of the automation
object in question to simulation model so that the parts of
the plant that don't need the resource being upgraded in the
production can continue to function, resolv the problem or
perform the upgrade and finally switch back. This feature
can also be used for active monitoring, tuning and control
of the system by a human operator given that the views
implementing the human machine interface are developed.
